|

### 2024-10-10 assignments/replication_exercise/replication_exercise.Rmd
lecture 12

- Some ideas for an extension are:
    - **Enhance the research question**: this could mean studying heterogeneity or 
    - **Robustness checks**: Verify the original results under different assumptions or specifications.
    - **Error identification and correction**: If you identify any mistakes in the original analysis, provide a corrected version with clear explanations.

>>>>

- Some ideas for an extension are:
    - **Enhance the research question**: this could mean studying heterogeneity or non-linearities.
    - **Robustness checks**: Verify the original results under different assumptions or specifications.
    - **Error identification and correction**: If you identify any mistakes in the original analysis, provide a corrected version with clear explanations.
